\textls[-0]{\thetitle}

### 2023-03-05 metatheory-condensed.tex
compress a little

%In dependent type system, types are treated as terms, and should have a type.
We use Tarski-style universes~\cite{hofmann1997syntax}:
a universe~$\cU$ is not inhabited by types directly\footnote{By contrast, 
Russel-style universes are inhabited by types directly. 
Tarski-style universes are ``semantically more fundamental'' \cite{luo2012notes} and friendlier to our meta-theoretical reasoning.},
but rather by the \emph{codes} of types:
$\codety{T}$ encodes type~$T$ (rule \ruleref{tm/c}),
and $\El{t}$ decodes~$t$ (rule \ruleref{ty/el}).
MLTT has an infinite hierarchy of universes;
we omit universe levels in the presentation for conciseness.
\rA{Why is W(t) a term and not a type?}\EDJreply{changed, please review.}\YZreply{I think the reviewer is wondering what is gained by encoding and decoding types, compared to types directly inhabiting universes.}\EDJ{changed again, please review.}

>>>>

%In dependent type system, types are treated as terms, and should have a type.
We use Tarski-style universes \cite{hofmann1997syntax}.
Unlike Russell-style universes, they
are not inhabited by types directly but rather by the \emph{codes} of types
and arguably behave better \cite{luo2012notes}.
$\codety{T}$ encodes type~$T$ (rule \ruleref{tm/c}) and thus inhabits~$\cU$.
$\El{t}$ decodes~$t$ (rule \ruleref{ty/el}).
%\footnote{By contrast,  Russel-style universes are inhabited by types directly.  Tarski-style universes are ``semantically more fundamental'' \cite{luo2012notes} and friendlier to our meta-theoretical reasoning.}
MLTT has an infinite hierarchy of universes;
we omit universe levels in the presentation for conciseness.
%\rA{Why is W(t) a term and not a type?}\YZreply{I think the reviewer is wondering what is gained by encoding and decoding types, compared to types directly inhabiting universes.}
